|

### 2021-10-11 index.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

ggsave("title_plot.jpg", title_plot, 
       width = 7, height = 5, units = "in")
```

@@

.pull-left[
![](title_plot.jpg)
]

@@

---
background-image: url("images/meteor.jpeg")
background-position: 90% 73%
background-size: 42%

@@

```{r, echo=FALSE, fig.align='center', out.width='95%', fig.retina=3}
knitr::include_graphics("images/mermaid.png")
```

@@

.panelset.sideways[
.panel[.panel-name[Introduction]
```{r, echo = FALSE, out.width='90%'}
knitr::include_graphics("images/introduction.png")
```
]
.panel[.panel-name[Prior Beliefs]

![](images/prior_beliefs.png)
]

@@

![](images/thanks.png)
]
]

@@

Participants had to wait 30 seconds before proceeding to the next slide. 
---
.panelset.sideways[
.panel[.panel-name[Study design & research approach (Single-analyst)]
```{r, echo = FALSE, out.width='93%'}
knitr::include_graphics("images/design_single.png")
```
]

.panel[.panel-name[Study design & research approach (Multi-analyst)]
```{r, echo = FALSE, out.width='91%'}
knitr::include_graphics("images/design_multi.png")
```
]
]

@@

.panelset[
.panel[.panel-name[Results (Single-analyst)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_single.png")
```
]

.panel[.panel-name[Results (Multi-consistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_multi-consistent.png")
```
]

.panel[.panel-name[Results (Multi-inconsistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("images/results_multi-inconsistent.png")
```
]
]

@@

.panelset.sideways[
.panel[.panel-name[Posterior beliefs]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/posterior_beliefs.png")
```
]

.panel[.panel-name[Credibility]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/credibility.png")
```
]

.panel[.panel-name[Confidence]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/confidence.png")
```
]

.panel[.panel-name[Bias]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]
.panel[.panel-name[Error]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]
.panel[.panel-name[Discretion]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/bias.png")
```
]

.panel[.panel-name[Attention check]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("images/attention.png")
```
]

@@

```{r, echo = FALSE, fig.retina=3, fig.align='center', out.width='110%'}
knitr::include_graphics("images/participants.png")
```

@@

---
background-image: url("images/Figure1.jpg")
background-position: 50% 50%
background-size: 78%

@@

---
background-image: url("images/Figure2.jpg")
background-position: 50% 50%
background-size: 78%

>>>>

ggsave("talk/title_plot.jpg", title_plot, 
       width = 7, height = 5, units = "in")
```

@@

.pull-left[
![](talk/title_plot.jpg)
]

@@

---
background-image: url("talk/meteor.jpeg")
background-position: 90% 73%
background-size: 42%

@@

```{r, echo=FALSE, fig.align='center', out.width='95%', fig.retina=3}
knitr::include_graphics("talk/mermaid.png")
```

@@

.panelset.sideways[
.panel[.panel-name[Introduction]
```{r, echo = FALSE, out.width='90%'}
knitr::include_graphics("talk/introduction.png")
```
]
.panel[.panel-name[Prior Beliefs]

![](talk/prior_beliefs.png)
]

@@

![](talk/thanks.png)
]
]

@@

Participants had to wait 30 seconds before proceeding to the next slide. 
---
.panelset.sideways[
.panel[.panel-name[Study design & research approach (Single-analyst)]
```{r, echo = FALSE, out.width='93%'}
knitr::include_graphics("talk/design_single.png")
```
]

.panel[.panel-name[Study design & research approach (Multi-analyst)]
```{r, echo = FALSE, out.width='91%'}
knitr::include_graphics("talk/design_multi.png")
```
]
]

@@

.panelset[
.panel[.panel-name[Results (Single-analyst)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("talk/results_single.png")
```
]

.panel[.panel-name[Results (Multi-consistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("talk/results_multi-consistent.png")
```
]

.panel[.panel-name[Results (Multi-inconsistent)]
```{r, echo = FALSE, out.width='80%'}
knitr::include_graphics("talk/results_multi-inconsistent.png")
```
]
]

@@

.panelset.sideways[
.panel[.panel-name[Posterior beliefs]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/posterior_beliefs.png")
```
]

.panel[.panel-name[Credibility]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/credibility.png")
```
]

.panel[.panel-name[Confidence]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/confidence.png")
```
]

.panel[.panel-name[Bias]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/bias.png")
```
]
.panel[.panel-name[Error]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/bias.png")
```
]
.panel[.panel-name[Discretion]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/bias.png")
```
]

.panel[.panel-name[Attention check]
```{r, echo = FALSE, out.width='100%'}
knitr::include_graphics("talk/attention.png")
```
]

@@

```{r, echo = FALSE, fig.retina=3, fig.align='center', out.width='110%'}
knitr::include_graphics("talk/participants.png")
```

@@

---
background-image: url("talk/Figure1.jpg")
background-position: 50% 50%
background-size: 78%

@@

---
background-image: url("talk/Figure2.jpg")
background-position: 50% 50%
background-size: 78%

### 2021-10-11 manuscript/manuscript.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

ggsave(paste0(here(), "/talk/images/Figure1.jpg"), p1, 
       width = 7, height = 5, units = "in") #save to talk folder

@@

ggsave(paste0(here(), "/talk/images/Figure2.jpg"), p2, 
       width = 7, height = 5, units = "in") #save to talk folder

>>>>

ggsave(paste0(here(), "/talk/Figure1.jpg"), p1, 
       width = 7, height = 5, units = "in") #save to talk folder

@@

ggsave(paste0(here(), "/talk/Figure2.jpg"), p2, 
       width = 7, height = 5, units = "in") #save to talk folder

### 2021-10-11 poster/GSPA_Abstract.Rmd
restructured repo (index.Rmd in root, to build a site for the slides)

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. However, as with any real-world intervention, scientific reform can have unintended consequences and impose high costs. While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom. Given the resource-intensity of crowdsourced data analysis, our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

>>>>

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. However, as with any real-world intervention, scientific reform can have unintended consequences and impose high costs. While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and researcher degrees of freedom. Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.
